<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{Installation}
-->

## Installation

This package is currently hosted on GitHub, so the easiest way to install the latest version is to use `devtools`. This install process will take some time since the BioGRID database will be downloaded and imported into a local SQLite database.

```{r eval = FALSE}
if (!require(devtools)) install.packages('devtools')
devtools::install_github('EricEdwardBryant/easydb')
devtools::install_github('EricEdwardBryant/biogridr')
```

## Using an archived version of BioGRID

If you want to use an archived version BioGRID you can specify the URL to the archive of interest using the `url` argument (use a link to the `tab2` format). BioGRID download URLs can be found [here](http://thebiogrid.org/download.php).

```{r eval = FALSE}
library(biogridr)
url <- paste0('http://thebiogrid.org/downloads/archives/Release%20Archive/',
              'BIOGRID-3.2.99/BIOGRID-ALL-3.2.99.tab2.zip')
update_biogridr(url = url)
```

If you want to save the interactions to a different local database (e.g. in your project's directory for use in your reproducible analysis), you can specify a path to this database with the `db` argument. By convention this path should end in `.sqlite`. In the example below, if `data/example.sqlite` does not exist, the biogridr package's database will be copied to this file, and interaction data will subsequently be downloaded and written to this new database.

```{r eval = FALSE}
# The path is relative to the current working directory
update_biogridr(db = 'data/example.sqlite')
```

To use this database by default, you may want to set the `biogridr.db` global option to point to your new database.

```{r eval = FALSE}
options(biogridr.db = 'data/example.sqlite')
src_biogridr()
```

## Why isn't the data just included in the package?

The dataset is well over 100 Mb, and with updates every few months, the git repository would swell to an unreasonable size. That said, this package makes it easy to setup a local copy of the BioGRID database.
