<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{usage examples}
-->

Welcome to the biogridr package!
================================

This package contains a SQLite database of BioGRID interactions. This vignette 
will demonstrate how to access this data.

```{r}
library(biogridr)

# Connect to the local BioGRID database
src_biogridr()
```

The database contains four tables:

- `interactions`: Interaction data in an edge list structure
- `log`: contains the BioGRID version number and download date
- `organisms`: A mapping of organism names to NCBI identifiers
- `systems`: Experimental systems (interaction classes) and their descriptions

To access a table you can use the `tbl` function. Don't be scared by all those 
`%>%`s (pronounced 'pipe')! Using `x %>% y` is equivalent to `f(x, y)` and just 
makes the syntax easier to read as a procedure, or 'pipeline', instead of a 
bunch of nested function calls, or a bunch of temporary variable assignments. 
You can use `collect` when you want to get your query returned as a data.frame 
(rather than a SQL query).

```{r message=FALSE, eval = FALSE}
# Some example genes of interest
genes <- c('CTF4', 'TOF1', 'MRC1', 'CSM3', 'RAD17', 'MEC3', 'DDC1')
yeast <- organism('cerevisiae')
```

```{r inner_net, eval = FALSE}
# Inner network example
example1 <-
  src_biogridr() %>%
  inner_net(genes, yeast) %>%
  aggregate

example1
example1 %>% plot()
example1 %>% plot('physical', bounds = c(-5,5), method = 'complete')
```

```{r outer_net, eval = FALSE}
# Outer network example
example2 <- 
  src_biogridr() %>%
  outer_net(genes, yeast) %>%
  aggregate

example2
example2 %>% plot()
```

Advanced queries with `dplyr`
---------------------------------

```{r eval = FALSE}
library(dplyr)
example2 <- 
  src_biogridr() %>%
  filter() %>%
  select() %>%
  group_by() %>%
  summarise()
```
